---
title: "AB Test Calculator"
author: "Aaron Mah"
date: "6/12/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
```

## AB Test Calculator

This AB Test Calculator takes multiple parameters from the user in order to evaluate whether a significant difference exists between the Control group and the Variant group. Users are shown a graphical representation of the confidence level and the distribution of both samples.

## User Controls

Users are able to control:

- Sample Size
- Conversion Events
- Type of Test (Two-sided, One-sided)
- Confidence Interval

## Assumptions

We assume independent events are being considered when entering conversion events. The standard deviation is calculated assuming a binomial distribution as such:
```{r cars, echo = TRUE, eval=FALSE}
errA <- sqrt((crA*(1-crA)/visitA))
errB <- sqrt((crB*(1-crB)/visitB))
```

```{r echo=FALSE, eval=TRUE, fig.width=3, fig.height=3}
        X <- seq(0, 1, by=0.01)
        Y <- dnorm(X, 0.2, sd=sqrt(.2*(1-.2)/100))
        Y2 <- dnorm(X, 0.6, sd=sqrt(.6*(1-.6)/100))
        qplot(X,Y, geom="line")+geom_line(aes(y=Y2))
```

## Additional Improvements

There are several visual/UX enhancements that may improve the overall usability:

- Better visual emphasis when a test is significant vs. not significant
- Responsive grid has quirky behaviour at certain screen sizes
- Additional context could be shown to the user as to how numbers are derived, methodology, etc.

Thanks!
